Trajectories

### 2022-09-13 index.qmd
Update report

---
title: "Trajectories"
subtitle: "Lab notes"
date: "Updated: `r format(Sys.Date(), '%Y/%m/%d')`"
format:
    html:
        abstract: "Bilinguals face the challenging task of learning words from languages with overlapping phonologies. Floccia et al. (2018) reported larger vocabulary sizes for 24-month-old bilinguals that were learning languages that shared a greater amount of cognates (e.g., English-Dutch). The mechanisms underlying this effect remain unknown. We explore two compatible scenarios. First, we test whether cognates are learnt earlier than non-cognates. This would account for the difference in vocabulary size associated to the amount of shared cognates across languages. Second, we explore the possibility that the word-forms of one language interact with those form the other language, scaffolding the acquisition of their translation equivalents when their phonologies overlap. This mechanism, in line with the parallel activation account of bilingual speech perception, would provide a plausible explanation to why cognates are acquired ealier by bilinguals. We developed an online tool to collect parental reports of receptive and productive vocabularies from children learning Catalan and/or Spanish, and present data on receptive and productive vocabulary of bilingual toddlers aged 12 to 34 months."
        toc: true
        smooth-scroll: true
        link-external-newwindow: true
        number-sections: true
        number-offset: 0
        code-fold: true
        code-overflow: scroll
        code-line-numbers: true
        code-copy: hover
        fig-dpi: 500
        reference-location: margin
        execute-dir: "C:/Users/U155880/Documents/trajectories/"
bibliography: "manuscript/references.bib"
csl: "manuscript/apa6.csl"
---

@@

library(bayesplot)
library(brms) 
library(conflicted)
library(dplyr) 
library(forcats)
library(ggplot2) 
library(ggsci)
library(gt) 
library(here) 
library(janitor)
library(knitr)
library(lubridate)
library(multilex)
library(patchwork) 
library(papaja) 
library(purrr)
library(scales) 
library(stringdist)
library(stringr)
library(targets)
library(tibble)
library(tidybayes) 
library(tidyr)

@@

We initially fitted a null model (`fit_0`) than only included the predictors `age` and `frequency` as nuisance parameters, along with random intercepts by `id` and `item`, and random slopes of `frequency` by `id`, and `age_std` by `item`, and their correlation parameter. We then expanded this model (`fit_1`) to include the main effect of `doe`, and the `doe` by `item` random slope. Finally, we added the main effect `cognate` (`fit_2`), its interaction with `doe` (`doe:cognate`), and random slopes for `cognate` by `id`.

@@

$$
\begin{aligned}\nu_{ij} = & \beta_0 +\beta_1\mathrm{Age}_{i} + \beta_2 \mathrm{Freq}_{j} + \beta_3\mathrm{Phon}_{j} + \beta_4\mathrm{Exposure}_{ij} + \beta_5 \mathrm{Levenshtein}_{j} +
\beta_6\mathrm{(Age_{i} \cdot \mathrm{Exposure}_{ij}}) + \beta_7\mathrm{(\mathrm{Age}_{i} \cdot \mathrm{Levenshtein}_{j}}) +  \beta_8\mathrm{(Exposure_{ij} \cdot \mathrm{Levenshtein}_{j}}) + 
\beta_9{(\mathrm{Age}_{i} \cdot \mathrm{Exposure}_{ij} \cdot \mathrm{Levenshtein}_{j}}) +\\

&\theta_{0j}^{(\mathrm{TE})} + \theta_{1j}^{(\mathrm{TE})}\mathrm{Age}_{i} +  \theta_{2j}^{(\mathrm{TE})} \mathrm{Freq}_{j} + \theta_{3j}^{(\mathrm{TE})} \mathrm{Phon}_{j} + \theta_{4j}^{(\mathrm{TE})} \mathrm{Exposure}_{ij} +  \theta_{5j}^{(\mathrm{TE})} (\mathrm{Age}_{i} \cdot \mathrm{Exposure}_{ij}) +\\

&\theta_{0j}^{(\mathrm{ID})} + \theta_{1j}^{(\mathrm{ID})}\mathrm{Age}_{i} +  \theta_{2j}^{(\mathrm{ID})} \mathrm{Freq}_{j} +   \theta_{3j}^{(\mathrm{ID})} \mathrm{Phon}_{j} + \theta_{4j}^{(\mathrm{ID})} \mathrm{Exposure}_{ij} + \theta_{5j}^{(\mathrm{ID})} \mathrm{Levenshtein}_{j} + \theta_{6j}^{(\mathrm{ID})} (\mathrm{Age}_{i} \cdot \mathrm{Exposure}_{ij}) + 
\theta_{7j}^{(\mathrm{ID})} (\mathrm{Age}_{i} \cdot \mathrm{Levenshtein}_{j}) +
\theta_{8j}^{(\mathrm{ID})} (\mathrm{Age}_{i} \cdot \mathrm{Exposure}_{ij} \cdot \mathrm{Levenshtein}_{j})\end{aligned}$$
:::

@@

In addition, we specified a $LKJ$ prior ($\sim LKJ(2)$ for the correlations between group-level coefficients. We implemented the model prior following {brms} syntax as:

@@

@@

-   OS: `r sessionInfo()$running`, `r`sessionInfo()\$platform\`
-   R version: `r sessionInfo()$R.version$version.string`
-   Algorithm: Hamiltonian Montecarlo (No U-turn Sampler, *NUTS*)
-   Engine: Stan (brms interface, `r sessionInfo()$otherPkgs$brms$Version`)
-   brms backend: CmdStanR (cmdstanr `r sessionInfo()$loadedOnly$cmdstanr$Version`)
-   Chains: `r dim(model_fit_7$fit)[2]`
-   Cores: `r dim(model_fit_7$fit)[2]`
-   Iterations: `r dim(model_fit_7$fit)[1]` (`r dim(model_fit_7$fit)[1]/2`)

@@

::: panel-tabset
### Model 0

@@

```{r}
print(model_fit_3$formula)
```

### Model 4

```{r}
print(model_fit_4$formula)
```

### Model 5

```{r}
print(model_fit_5$formula)
```

### Model 6

```{r}
print(model_fit_6$formula)
```

### Model 7

```{r}
print(model_fit_7$formula)
```
:::

@@

::: panel-tabset
### Model 0

```
// generated with brms 2.16.1
functions {
/* cratio-logit log-PDF for a single response
* Args:
*   y: response category
*   mu: latent mean parameter
*   disc: discrimination parameter
*   thres: ordinal thresholds
* Returns:
*   a scalar to be added to the log posterior
*/
real cratio_logit_lpmf(int y, real mu, real disc, vector thres) {
int nthres = num_elements(thres);
vector[nthres + 1] p;
vector[nthres] q;
int k = 1;
while (k <= min(y, nthres)) {
q[k] = log_inv_logit(disc * (mu - thres[k]));
p[k] = log1m_exp(q[k]);
for (kk in 1:(k - 1)) p[k] = p[k] + q[kk];
k += 1;
}
if (y == nthres + 1) {
p[nthres + 1] = sum(q);
}
return p[y];
}
/* cratio-logit log-PDF for a single response and merged thresholds
* Args:
*   y: response category
*   mu: latent mean parameter
*   disc: discrimination parameter
*   thres: vector of merged ordinal thresholds
*   j: start and end index for the applid threshold within 'thres'
* Returns:
*   a scalar to be added to the log posterior
*/
real cratio_logit_merged_lpmf(int y, real mu, real disc, vector thres, int[] j) {
return cratio_logit_lpmf(y | mu, disc, thres[j[1]:j[2]]);
}
}
data {
int<lower=1> N;  // total number of observations
int Y[N];  // response variable
int<lower=2> nthres;  // number of thresholds
// data for group-level effects of ID 1
int<lower=1> N_1;  // number of grouping levels
int<lower=1> M_1;  // number of coefficients per level
int<lower=1> J_1[N];  // grouping indicator per observation
// group-level predictor values
vector[N] Z_1_1;
// data for group-level effects of ID 2
int<lower=1> N_2;  // number of grouping levels
int<lower=1> M_2;  // number of coefficients per level
int<lower=1> J_2[N];  // grouping indicator per observation
// group-level predictor values
vector[N] Z_2_1;
int prior_only;  // should the likelihood be ignored?
}
transformed data {
}
parameters {
vector[nthres] Intercept;  // temporary thresholds for centered predictors
vector<lower=0>[M_1] sd_1;  // group-level standard deviations
vector[N_1] z_1[M_1];  // standardized group-level effects
vector<lower=0>[M_2] sd_2;  // group-level standard deviations
vector[N_2] z_2[M_2];  // standardized group-level effects
}
transformed parameters {
real<lower=0> disc = 1;  // discrimination parameters
vector[N_1] r_1_1;  // actual group-level effects
vector[N_2] r_2_1;  // actual group-level effects
r_1_1 = (sd_1[1] * (z_1[1]));
r_2_1 = (sd_2[1] * (z_2[1]));
}
model {
// likelihood including constants
if (!prior_only) {
// initialize linear predictor term
vector[N] mu = rep_vector(0.0, N);
for (n in 1:N) {
// add more terms to the linear predictor
mu[n] += r_1_1[J_1[n]] * Z_1_1[n] + r_2_1[J_2[n]] * Z_2_1[n];
}
for (n in 1:N) {
target += cratio_logit_lpmf(Y[n] | mu[n], disc, Intercept);
}
}
// priors including constants
target += normal_lpdf(Intercept | -0.25, 0.1);
target += normal_lpdf(sd_1 | 1, 0.1)
- 1 * normal_lccdf(0 | 1, 0.1);
target += std_normal_lpdf(z_1[1]);
target += normal_lpdf(sd_2 | 1, 0.1)
- 1 * normal_lccdf(0 | 1, 0.1);
target += std_normal_lpdf(z_2[1]);
}
generated quantities {
// compute actual thresholds
vector[nthres] b_Intercept = Intercept;
// additionally sample draws from priors
real prior_Intercept = normal_rng(-0.25,0.1);
real prior_sd_1 = normal_rng(1,0.1);
real prior_sd_2 = normal_rng(1,0.1);
// use rejection sampling for truncated priors
while (prior_sd_1 < 0) {
prior_sd_1 = normal_rng(1,0.1);
}
while (prior_sd_2 < 0) {
prior_sd_2 = normal_rng(1,0.1);
}
}
```
mu[n] += r_1_1[J_1[n]] * Z_1_1[n] + r_1_2[J_1[n]] * Z_1_2[n] + r_2_1[J_2[n]] * Z_2_1[n] + r_2_2[J_2[n]] * Z_2_2[n];
- 2 * normal_lccdf(0 | 1, 0.1);
- 2 * normal_lccdf(0 | 1, 0.1);
mu[n] += r_1_1[J_1[n]] * Z_1_1[n] + r_1_2[J_1[n]] * Z_1_2[n] + r_1_3[J_1[n]] * Z_1_3[n] + r_2_1[J_2[n]] * Z_2_1[n] + r_2_2[J_2[n]] * Z_2_2[n];
- 3 * normal_lccdf(0 | 1, 0.1);
- 2 * normal_lccdf(0 | 1, 0.1);
mu[n] += r_1_1[J_1[n]] * Z_1_1[n] + r_1_2[J_1[n]] * Z_1_2[n] + r_1_3[J_1[n]] * Z_1_3[n] + r_1_4[J_1[n]] * Z_1_4[n] + r_2_1[J_2[n]] * Z_2_1[n] + r_2_2[J_2[n]] * Z_2_2[n] + r_2_3[J_2[n]] * Z_2_3[n] + r_2_4[J_2[n]] * Z_2_4[n];
- 4 * normal_lccdf(0 | 1, 0.1);
- 4 * normal_lccdf(0 | 1, 0.1);

### Model 4

@@

### Model 5

@@

### Model 6

@@

### Model 7

@@

```{r}
#| label: results-raw
#| echo: true
#| message: false
#| warning: false
#| fig-width: 7
#| fig-height: 4
df %>%
    mutate(
        lv = cut_interval(lv, 5),
        age = floor(age)
    ) %>% 
    count(lv, age, response) %>%
    mutate(prop = n/sum(.$n)) %>% 
    ggplot(aes(age, prop, colour = response, fill = response)) +
    facet_wrap(~lv, nrow = 1) +
    geom_col(position = position_fill()) +
    geom_hline(yintercept = 0.5, colour = "black", size = 0.5) +
    labs(
        x = "Age (months)",
        y = "% responses", 
        colour = "Response",
        fill = "Response"
    ) +
    scale_fill_d3() +
    scale_colour_d3() +
    scale_x_continuous(breaks = seq(0, 40, 2)) +
    scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
    theme(
        legend.position = "top",
        axis.text.y = element_text(size = 7),
        axis.text.x = element_text(size = 7),
        axis.ticks.y = element_blank(),
        panel.grid = element_blank()
    )
```

@@

```{r}
#| label: results-loos
#| echo: true
#| message: false
#| warning: false
#| eval: false
#| fig-width: 7
model_loos %>% 
    as_tibble() %>% 
    rownames_to_column("model") %>% 
    relocate(
        model, 
        matches("elpd_loo"),
        matches("p_loo"), 
        matches("looic"), 
        matches("diff")
    ) %>%
    mutate_all(as.numeric) %>% 
    gt() %>% 
    tab_spanner(md("**LOO<sub>ELPD</sub>**"), matches("elpd_loo")) %>% 
    tab_spanner(md("**LOO<sub>p</sub>**"), matches("p_loo")) %>% 
    tab_spanner(md("**LOO<sub>IC</sub>**"), matches("looic")) %>% 
    tab_spanner(md("**LOO<sub>diff</sub>**"), matches("diff")) %>% 
    fmt_number(3:13) %>% 
    cols_label(
        model = "Model",
        # elpd
        elpd_loo = md("*ELPD*"),
        se_elpd_loo = md("*SE*"),
        subsampling_se_elpd_loo = md("*SE<sub>sub</sub>*"),
        # p
        p_loo = md("*p*"),
        se_p_loo = md("SE"),
        subsampling_se_p_loo = md("SE<sub>sub</sub>"),
        # looic
        looic = md("*LOO-IC*"),
        se_looic = md("*SE*"),
        subsampling_se_looic = md("SE<sub>sub</sub>"),
        # diff
        elpd_diff = md("*diff*"),
        se_diff = md("*SE*"),
        subsampling_se_diff = md("*SE<sub>sub</sub>*"),
    ) 
```

@@

```{r}
#| label: results-fixed-table
#| echo: true
#| message: false
#| warning: false
#| fig-width: 7
str_repl <- c(
    "age_std:doe_std:lv_std" = "Age \u00d7 DoE \u00d7 Levenshtein",
    "age_std:doe_std" = "Age \u00d7 DoE",
    "age_std:lv_std" = "Age \u00d7 Levenshtein",
    "doe_std:lv_std" = "DoE \u00d7 Levenshtein",
    "Intercept" = "Intercept",
    "age_std" = "Age (+1 month)",
    "freq_std" = "Frequency (+1 SD)",
    "n_phon_std" = "# Phonemes (+1 SD)",
    "doe_std" = "DoE (+10%)",
    "lv_std" = "Levenshtein (+1 SD)"
)

draws_fix <- fixef(model_fit_7) %>% 
    as.data.frame() %>%
    rownames_to_column("term") %>% 
    clean_names() %>% 
    select(-est_error) %>% 
    mutate(
        estimate = ifelse(term=="Intercept", inv_logit_scaled(estimate), estimate/4),
        q2_5 = ifelse(term=="Intercept", inv_logit_scaled(q2_5), q2_5/4),
        q97_5 = ifelse(term=="Intercept", inv_logit_scaled(q97_5), q97_5/4),
        term = str_replace_all(term, str_repl)
    )

gt(draws_fix) %>% 
    fmt_percent(2) %>% 
    fmt_number(3:4, decimals = 2) %>% 
    cols_merge(vars("q2_5", "q97_5"), pattern = "[{1}, {2}]") %>% 
    cols_label(
        term = md("**Predictor**"),
        estimate = md("**Mean**"),
        q2_5 = md("**95\\% CrI**"),
    ) %>% 
    tab_footnote(
        footnote = "Transformed using the inverse logit to get the average probability of correct response",
        locations = cells_body(columns = "term", rows = term=="Intercept")
    ) %>% 
    tab_footnote(
        footnote = "Transformed using the divide-by-four- rule to get the maximum change in probability of correct response, associated with a unit increase in this variable.",
        locations = cells_body(columns = "term", rows = term %in% c("Age (+1 month)", "Frequency (+ 1 SD)",  "DoE (+10%)", "Levenshtein (+ 1 SD)", "doe_std:lv_std" = "DoE \u00d7 Levenshtein"))
    ) %>% 
    cols_align(
        align = c("center"),
        columns = 2:3
    )
```

>>>>

---
title: "Trajectories"
subtitle: "Lab notes"
date: "Updated: `r format(Sys.Date(), '%Y/%m/%d')`"
authors:
  - name: Gonzalo Garcia-Castro
    orcid: 0000-0002-8553-4209
    email: gonzalo.garciadecastro@upf.edu
    corresponding: true
    affiliations:
      - name: Universitat Pompeu Fabra
        department: Center for Brain and Cognition
        address: Ramon Trias fargas 25-27
        city: Barcelona
        state: Spain
        postal-code: 08005
  - name: Daniela S. Ávila-Varela
    orcid: 0000-0002-3518-8117
    affiliations:
      - name: Universitat Pompeu Fabra
        department: Center for Brain and Cognition
  - name: Ignacio Castillejo
    orcid: 0000-0001-7445-0416
    affiliations:
      - name: Universidad Atónoma de Madrid
        department: Departamento de Psicología
  - name: Nuria Sebastian-Galles
    orcid: 0000-0001-6938-2498
    affiliations:
      - name: Universitat Pompeu Fabra
        department: Center for Brain and Cognition
abstract: "Bilinguals face the challenging task of learning words from languages with overlapping phonologies. Floccia et al. (2018) reported larger vocabulary sizes for 24-month-old bilinguals that were learning languages that shared a greater amount of cognates (e.g., English-Dutch). The mechanisms underlying this effect remain unknown. We explore two compatible scenarios. First, we test whether cognates are learnt earlier than non-cognates. This would account for the difference in vocabulary size associated to the amount of shared cognates across languages. Second, we explore the possibility that the word-forms of one language interact with those form the other language, scaffolding the acquisition of their translation equivalents when their phonologies overlap. This mechanism, in line with the parallel activation account of bilingual speech perception, would provide a plausible explanation to why cognates are acquired ealier by bilinguals. We developed an online tool to collect parental reports of receptive and productive vocabularies from children learning Catalan and/or Spanish, and present data on receptive and productive vocabulary of bilingual toddlers aged 12 to 34 months."
format:
    html:
        toc: true
        smooth-scroll: true
        link-external-newwindow: true
        number-sections: true
        number-offset: 0
        code-fold: true
        code-overflow: scroll
        code-line-numbers: true
        code-copy: hover
        fig-dpi: 500
        reference-location: margin
        execute-dir: "C:/Users/U155880/Documents/trajectories/"
bibliography: "manuscript/references.bib"
csl: "manuscript/apa6.csl"
---

@@

library(bayesplot)
library(brms) 
library(conflicted)
library(dplyr) 
library(forcats)
library(ggplot2) 
library(marginaleffects)
library(ggsci)
library(gt) 
library(here) 
library(janitor)
library(knitr)
library(lubridate)
library(multilex)
library(patchwork) 
library(papaja) 
library(purrr)
library(scales) 
library(stringdist)
library(stringr)
library(targets)
library(tibble)
library(tidybayes) 
library(tidyr)

@@

## Model comparison

We initially fitted a base model (`model_fit_0`) that only included the predictors $Age$ (`age_std`), $Frequency$ (`freq_std`), $Phonemes$ (`n_phon_std`), and $DoE$ (`doe_std`) as nuisance parameters, along with random intercepts and slopes of all predictors by $Participant$ (`id`) and $Item$ (`te`), and all correlation parameters. We then expanded this model by adding the main effect of $Levenshtein$ (`lv_std`) (`model_fit_1`) and its random slope by $Participant$. Then, we added the $DoE \times Levenshtein$ (`doe_std:lv_std`) two-way interaction (`model_fit_2`) and its random slope by $Participant$. Finally, we added the $Age \times Levenshtein$ (`age_std:doe_std:lv_std`) three-way interaction with its random slope by $Participant$, along with a random slope for the $Age \times DoE$ (`age_std:doe_std`) two-way interaction.

@@

$$\begin{aligned}
\nu_{ij} = & \beta_0 +\beta_1\mathrm{Age}_{i} + \beta_2 \mathrm{Freq}_{j} + \beta_3\mathrm{Phon}_{j} + \beta_4\mathrm{Exposure}_{ij} + \beta_5 \mathrm{Levenshtein}_{j} + & [\mbox{Main effects}]\\
&\beta_6\mathrm{(Age_{i} \cdot \mathrm{Exposure}_{ij}}) + \beta_7\mathrm{(\mathrm{Age}_{i} \cdot \mathrm{Levenshtein}_{j}}) +  \beta_8\mathrm{(Exposure_{ij} \cdot \mathrm{Levenshtein}_{j}}) + & [\mbox{Two-way interactions}]\\
&\beta_9{(\mathrm{Age}_{i} \cdot \mathrm{Exposure}_{ij} \cdot \mathrm{Levenshtein}_{j}}) + & [\mbox{Three-way interaction}]\\

&\theta_{0j}^{(\mathrm{TE})} + \theta_{1j}^{(\mathrm{TE})}\mathrm{Age}_{i} +  \theta_{2j}^{(\mathrm{TE})} \mathrm{Freq}_{j} + \theta_{3j}^{(\mathrm{TE})} \mathrm{Phon}_{j} + \theta_{4j}^{(\mathrm{TE})} \mathrm{Exposure}_{ij} +  \theta_{5j}^{(\mathrm{TE})} (\mathrm{Age}_{i} \cdot \mathrm{Exposure}_{ij}) + & [\mbox{Item-level effects}]\\

&\theta_{0j}^{(\mathrm{ID})} + \theta_{1j}^{(\mathrm{ID})}\mathrm{Age}_{i} +  \theta_{2j}^{(\mathrm{ID})} \mathrm{Freq}_{j} +   \theta_{3j}^{(\mathrm{ID})} \mathrm{Phon}_{j} + \theta_{4j}^{(\mathrm{ID})} \mathrm{Exposure}_{ij} + \theta_{5j}^{(\mathrm{ID})} \mathrm{Levenshtein}_{j} + \theta_{6j}^{(\mathrm{ID})} (\mathrm{Age}_{i} \cdot \mathrm{Exposure}_{ij}) & [\mbox{Participant-level effects}]
\end{aligned}$$
:::

@@

In addition, we specified a $LKJ$ prior--$\sim LKJ(2)$ for the correlations between group-level coefficients. We implemented the model prior following {brms} syntax as:

@@

### Prior predictions

```{r}
#| label: prior-predictions
#| echo: true
#| message: false
#| warning: false
#| fig-width: 7
nd <- expand.grid(
    n_phon_std = 0,
    freq_std = 0,
    age_std = (10:36-mean(df$age))/(sd(df$age)),
    doe_std = 0,
    lv_std = 0
)

m <- add_epred_draws(nd, model_fit_3_prior, ndraws = NULL, re_formula = NA) %>% 
    filter(.category != "No") %>% 
    pivot_wider(names_from = ".category", values_from = ".epred") %>% 
    mutate(Understands = Understands + `Understands and Says`) %>% 
    pivot_longer(
        c(Understands, `Understands and Says`),
        names_to = ".category",
        values_to = ".epred"
    ) %>% 
    mutate(
        .category = factor(
            .category,
            levels = c("Understands and Says", "Understands"),
            labels = c("Production\n(Understands and Says))", "Comprehension\n(Understands)")
        )
    )

m %>% 
    ggplot() +
    aes(
        x = age_std, 
        y = .epred, 
    ) +
    facet_wrap(~.category) +
    # geom_line(
    #     aes(group = interaction(.draw)),
    #     alpha = 0.05,
    #     size = 1
    # ) +
    stat_lineribbon(size = 1, colour = NA, .width = c(0.95, 0.89, 0.67, 0.5)) +
    stat_summary(fun = "mean", geom = "line", size = 0.75) +
    scale_x_continuous(
        breaks = (seq(10, 36, 4)-mean(df$age))/(sd(df$age)),
        labels = seq(10, 36, 4),
        sec.axis = dup_axis(
            name = "Age (years; months)",
            labels = months_to_years(
                rescale_variable(
                    (seq(10, 36, 4)-mean(df$age))/(sd(df$age)),
                    mean(df$age),
                    sd(df$age)
                )
            )
        )
    ) +
    scale_fill_brewer(
        palette = "YlOrRd",
        labels = c("95%", "89%", "67%", "50%")
    ) +
    labs(
        x = "Age (months)", 
        y = "Probability of acquisition\n(Linear prediction)",
        colour = "Credible interval", 
        fill = "Credible interval"
    ) +
    scale_y_continuous(labels = percent, limits = c(0, 1)) +
    theme(
        legend.position = "top",
        axis.ticks.x = element_line(colour = "black"),
        panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.border = element_rect(fill = NA, colour = "black", size = 0.75),
        strip.background = element_rect(fill = "grey", colour = NA),
        plot.background = element_rect(fill = "white", colour = NA)
    )
```

@@

-   OS: `r sessionInfo()$running`, `r sessionInfo()$platform`
-   R version: `r sessionInfo()$R.version$version.string`
-   Algorithm: Hamiltonian Montecarlo (No U-turn Sampler, *NUTS*)
-   Engine: Stan (brms interface, `r sessionInfo()$otherPkgs$brms$Version`)
-   brms backend: CmdStanR (cmdstanr `r sessionInfo()$loadedOnly$cmdstanr$Version`)
-   Chains: `r dim(model_fit_7$fit)[2]`
-   Cores: `r dim(model_fit_7$fit)[2]`
-   Iterations: `r format(dim(model_fit_7$fit)[1], big.mark = ",")` (`r format(dim(model_fit_7$fit)[1]/2, big.mark = ",")`)

@@

::: panel-tabset

### Model 0

@@

```{r}
print(model_fit_3$formula)
```
:::

@@

::: panel-tabset

### Model 0

@@

@@

@@

@@

```{r}
#| label: results-raw
#| echo: true
#| message: false
#| warning: false
#| fig-width: 7
df %>%
    mutate(
        lv = cut_interval(lv*100, 5) %>% 
            gsub("([0-9.]+)", "\\1%", .) %>% 
            factor(levels = c("[0%,20%]", "(20%,40%]", "(40%,60%]", "(60%,80%]", "(80%,100%]")),
        doe = cut_interval(doe*100, 3) %>% 
            gsub("([0-9.]+)", "\\1%", .) %>% 
            factor(levels = c("[0%,33.3%]", "(33.3%,66.7%]", "(66.7%,100%]")) %>% 
            paste0("Degree of Exposure: ", .) %>% 
            factor(
                levels = paste0(
                    "Degree of Exposure: ", 
                    c("[0%,33.3%]", "(33.3%,66.7%]", "(66.7%,100%]")
                )
            ),
        age = floor(age),
        Understands = response %in% c("Understands", "Understands and Says"),
        `Understands and Says` = response %in% c("Understands and Says")
    ) %>% 
    group_by(te, lv, age, doe) %>%
    summarise(
        n = n(),
        Understands = mean(Understands),
        `Understands and Says` = mean(`Understands and Says`),
        .groups = "drop"
    ) %>% 
    pivot_longer(
        c(Understands, `Understands and Says`), 
        names_to = ".category", 
        values_to = "prop"
    ) %>% 
    group_by(lv, age, doe, .category) %>%
    summarise(
        n = sum(n),
        prop = mean(prop),
        .groups = "drop"
    ) %>% 
    mutate(
        prop_se = sd(prop)/sqrt(n),
        prop_lower = prop-prop_se,
        prop_upper = prop+prop_se,
        prop_lower = ifelse(prop_lower < 0, 0, prop_lower),
        prop_upper = ifelse(prop_upper >1, 1, prop_upper)
    ) %>% 
    ggplot() +
    aes(age, prop, colour = lv, fill = lv, shape = lv) +
    facet_grid(.category~doe) +
    geom_hline(yintercept = 0.5, colour = "grey", size = 0.5) +
    geom_line(size = 1, alpha = 0.75) +
    # geom_point(size = 2) +
    labs(
        x = "Age (months)",
        y = "Proportion of responses", 
        colour = "Phonological similarity (Levenshtein)",
        fill = "Phonological similarity (Levenshtein)",
        shape = "Phonological similarity (Levenshtein)",
        linetype = "Phonological similarity (Levenshtein)"
    ) +
    scale_color_brewer() +
    # scale_colour_manual(values = wesanderson::wes_palette("Zissou1", n = 5, type = "continuous")[1:5]) +
    scale_x_continuous(breaks = seq(0, 40, 4)) +
    scale_y_continuous(limits = c(0, 1), labels = percent) +
    theme(
        legend.position = "top",
        axis.ticks.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.border = element_rect(fill = NA, colour = "black", size = 0.75),
        plot.background = element_rect(fill = "white", colour = NA),
        strip.background = element_rect(fill = "grey", colour = "grey")
    )

ggsave("plot.png", height = 6, width = 9)
```

@@

```{r}
#| label: results-loos
#| echo: true
#| message: false
#| warning: false
#| eval: false
#| fig-width: 7
model_loos %>% 
    loo_compare() %>% 
    as.data.frame() %>%   
    rownames_to_column("model") %>% 
    relocate(
        model, 
        matches("elpd_loo"),
        matches("p_loo"), 
        matches("looic"), 
        matches("diff")
    ) %>%
    gt() %>% 
    tab_spanner(md("**LOO<sub>ELPD</sub>**"), matches("elpd_loo")) %>% 
    tab_spanner(md("**LOO<sub>p</sub>**"), matches("p_loo")) %>% 
    tab_spanner(md("**LOO<sub>IC</sub>**"), matches("looic")) %>% 
    tab_spanner(md("**LOO<sub>diff</sub>**"), matches("diff")) %>% 
    fmt_number(2:9) %>% 
    cols_label(
        model = "Model",
        # elpd
        elpd_loo = md("*ELPD*"),
        se_elpd_loo = md("*SE*"),
        # p
        p_loo = md("*p*"),
        se_p_loo = md("SE"),
        # looic
        looic = md("*LOO-IC*"),
        se_looic = md("*SE*"),
        # diff
        elpd_diff = md("*diff*"),
        se_diff = md("*SE*")
    ) %>% 
    tab_source_note(md("Pareto-*k* estimates of all models were acceptable (*k* < 0.5)"))
```

### Leave-one-out diagnostics (Pareto-*k* diagnostics)

::: panel-tabset

#### Model 0

```{r}
#| label: loo-diagnostics-0
#| echo: true
#| message: false
#| warning: false
#| fig-width: 7
get_loo_plot <- function(x){
    x$pointwise[,5] %>% 
        data.frame(x = 1:length(.), y = .) %>% 
        ggplot(aes(x, y)) +
        geom_point(
            size = 0.5, alpha = 0.1, colour = pal_d3()(3)[2], 
            shape = 1
        ) +
        geom_hline(yintercept = 0.5, linetype = "dotted") +
        labs(
            x = "Data point",
            y = "Pareto-k value",
            title = "PSIS diagnostic plot"
        ) +
        scale_x_continuous(breaks = seq(0, length(x$pointwise[,5]), 50000)) +
        scale_y_continuous(
            limits = c(-0.6, 0.6)
        )
}

get_loo_plot(model_loos$model_fit_0)
```

#### Model 1

```{r}
#| label: loo-diagnostics-1
#| echo: true
#| message: false
#| warning: false
#| fig-width: 7
get_loo_plot(model_loos$model_fit_1)
```

#### Model 2

```{r}
#| label: loo-diagnostics-2
#| echo: true
#| message: false
#| warning: false
#| fig-width: 7
get_loo_plot(model_loos$model_fit_2)
```

#### Model 3

```{r}
#| label: loo-diagnostics-3
#| echo: true
#| message: false
#| warning: false
#| fig-width: 7
get_loo_plot(model_loos$model_fit_3)
```

@@

```{r}
#| label: results-fixed-table
#| echo: true
#| message: false
#| warning: false
#| fig-width: 7
str_repl <- c(
    "Intercept\\[1\\]" = paste0("Intercept (Comprehension and Production at ",  round(mean(df$age, 2)), " months)"),
    "Intercept\\[2\\]" = paste0("Intercept (Comprehension at ", round(mean(df$age, 2)), " months)"),
    "age_std:doe_std:lv_std" = "Age \u00d7 DoE \u00d7 Levenshtein",
    "age_std:doe_std" = "Age \u00d7 DoE",
    "age_std:lv_std" = "Age \u00d7 Levenshtein",
    "doe_std:lv_std" = "DoE \u00d7 Levenshtein",
    "age_std" = paste0("Age (+1 SD, ",  round(sd(df$age), 2), " months)"),
    "freq_std" = paste0("Frequency (+1 SD, ",  round(sd(df$freq), 2), " Zipf)"),
    "n_phon_std" = paste0("Phonemes (+1 SD, ",  round(sd(df$n_phon), 2), " phonemes)"),
    "doe_std" = paste0("DoE (+1 SD, ",  percent(sd(df$doe)), ")"),
    "lv_std" = paste0("Levenshtein (+1 SD, ",  percent(sd(df$lv)), ")")
)

intercept_footnote <- paste0(
    "Probability of comprehension or production at the average age of the sample (", round(mean(df$age), 2), " months), transformed to the probability scale using the inverse logit."
)

slopes_footnote <- "Transformed using the divide-by-four rule to get the maximum change in probability of correct response, associated with a unit increase in this variable."

draws_fix <- fixef(model_fit_3) %>% 
    as.data.frame() %>%
    rownames_to_column("term") %>% 
    clean_names() %>% 
    select(-est_error) %>% 
    mutate(
        estimate_p = ifelse(grepl("Intercept", term), plogis(estimate), estimate/4),
        q2_5_p = ifelse(grepl("Intercept", term), plogis(q2_5), q2_5/4),
        q97_5_p = ifelse(grepl("Intercept", term), plogis(q97_5), q97_5/4),
        term = str_replace_all(term, str_repl),
        group = ifelse(grepl("Intercept", term), "Intercepts", "Slopes")
    )

gt(draws_fix, rowname_col = "term") %>% 
    fmt_number(2:7, decimals = 2) %>% 
    cols_merge(c("q2_5", "q97_5"), pattern = "[{1}, {2}]") %>% 
    cols_merge(c("q2_5_p", "q97_5_p"), pattern = "[{1}, {2}]") %>% 
    tab_spanner("Logit scale", c(estimate, q2_5, q97_5)) %>% 
    tab_spanner("Probability scale", c(estimate_p, q2_5_p, q97_5_p)) %>% 
    tab_row_group(label = "Intercepts", rows = 1:2) %>% 
    tab_row_group(label = "Slopes", rows = 3:nrow(draws_fix)) %>% 
    row_group_order(groups = c("Intercepts", "Slopes")) %>% 
    cols_label(
        term = md("**Predictor**"),
        estimate = "Mean",
        q2_5 = md("95\\% CrI"),
        estimate_p = "Mean",
        q2_5_p = md("95\\% CrI"),
    ) %>% 
    tab_footnote(
        footnote = intercept_footnote,
        locations = cells_body(
            columns = "term", 
            rows = grepl("Intercept", term)
        )
    ) %>% 
    tab_footnote(
        footnote = slopes_footnote,
        locations = cells_body(
            columns = "term", 
            rows = term %in% str_repl[-c(1, 2)]
        )
    ) %>% 
    cols_align(
        align = c("right"),
        columns = 2:7
    ) %>% 
    tab_style(
        cell_text(weight = "bold"),
        cells_column_spanners(everything())
    ) %>% 
    tab_style(
        list(cell_text(style = "italic"), cell_fill(color = "grey")),
        cells_row_groups()
    ) %>% 
    cols_hide(group)
```
